### 2024-03-23 src/data_prep/data_prep.Rmd
change file location for outputs

```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
movie_data <- read_csv("movie_data.csv")

@@

```{r save file}
write_csv(movie_data, "movie_data_cleaned.csv")
```

>>>>

```{r reformatting the data, message=FALSE, warning=FALSE, include=FALSE}
movie_data <- read_csv("data/movie_data.csv")

@@

```{r save file}
write_csv(movie_data, "data/movie_data_cleaned.csv")
```
